SPARQL on the open, decentralised Web

### 2016-06-02 dissertation/motivation.tex
dev motivation

@@

>>>>

The following section provides an overview of the motivation behind
this work in general and each direction in particular. Detailed
problem statements are given in Section~\ref{sec:problems}.

@@

\subsection{Developer friendliness}

As noted, my hypermedia motivation came from the perspective as a
developer, but hypermedia has a substantial research literature behind
it. While software engineering certainly is a large field, the
direction of work concerning developer friendliness comes mainly from
personal experience, from developing solutions in the industry, but
also from working with other developers who are at best indifferent to
Semantic Web technologies, and in many cases antagonistic towards it. 
As noted in Section~\ref{sec:history}, Aaron Swartz echoed the
sentiment already a decade ago that the Semantic Web had failed
because it did not provide tangible benefits, and had gotten a
reputation for being unfriendly to developers. It is crucial to
address this problem.
